A practical guide for selecting the spectral photon flux density distribution of light for comparing photosynthetic rates of leaves grown under different spectral light environments

### 2016-08-04 Header.Rmd
英文構成を依頼 (Edanz)。3089 words

---
title: "A guide for selecting the spectral photon flux density distribution of light for comparing photosynthetic rates of leaves grown under different spectral light environments"
author: "Keach Murakami^1\\*^, Ryo Matsuda^1^, Kazuhiro Fujiwara^1^"
bibliography: ~/GitHub/BeeLabR/BibTex/with.bib
csl: ECB.csl
header-includes:
  - \setmainfont{Helvetica}
  - \usepackage{zxjatype} # 日本語を使う
  - \setjamainfont{Hiragino Kaku Gothic Pro} # 日本語フォント
  - \usepackage{lscape} # 図を回転する
  - \newcommand{\blandscape}{\begin{landscape}} # 図回転用のbegin command
  - \newcommand{\elandscape}{\end{landscape}} # 図回転用のend command
  - \usepackage{setspace} # 行間の調節
  - \newcommand{\bdoublespace}{\begin{spacing}{1.5}} # 行間を広げるbegin command
  - \newcommand{\edoublespace}{\end{spacing}{1.5}} # 行間を広げるbegin command

@@

>>>>

---
title: "Evaluating effects of light quality: A basis for selecting the spectral photon flux density distribution of light for measuring photosynthetic rates of leaves"
author: "Keach Murakami^1\\*^, Ryo Matsuda^1^, Kazuhiro Fujiwara^1^"
bibliography: ~/GitHub/BeeLabR/BibTex/with.bib
csl: ECB.csl
header-includes:
  - \setmainfont{Helvetica}
  - \usepackage{zxjatype} # 日本語を使う
  - \setjamainfont{Hiragino Kaku Gothic Pro} # 日本語フォント
  - \usepackage{lscape} # 図を回転する
  - \newcommand{\blandscape}{\begin{landscape}} # 図回転用のbegin command
  - \newcommand{\elandscape}{\end{landscape}} # 図回転用のend command
  - \usepackage{setspace} # 行間の調節
  - \newcommand{\bdoublespace}{\begin{spacing}{1.5}} # 行間を広げるbegin command
  - \newcommand{\edoublespace}{\end{spacing}{1.5}} # 行間を広げるbegin command

@@

Affiliations: ^1^Graduate School of Agricultural and Life Sciences, The University of Tokyo

Address: ^1^Yayoi, Bunkyo, Tokyo, 113--8657, Japan

e-mail: keach.murakami@gmail.com

------

**Abstract**

  The spectral photon flux density distribution (SPD) of light during growth and for measurements do not only directly affect the net photosynthetic rate (*P*~n~) but also interacts on it.
  A plausible mechanisms of the interaction, some situations in which the interaction should be concerned, and the selection of appropriate measuring light for evaluation of photosynthesis are summarized.
  *P*~n~ should be measured under *in situ* conditions depending on the purpose of the study.
  In prospective studies focusing on plant growth after the measurements, the measurements should be made under the SPD of light that the plant will be subject to.
  In retrospective studies aiming to elucidate causes of differences between the experimental groups, the measurements should be made under the SPDs of light that the plants have received during the treatments.
  In descriptive studies, *P*~n~ should be evaluated under several SPDs of measuring light to comprehend general photosynthetic characteristics of the leaves.
  *P*~n~ under a single-pattern SPD of measuring light is only an aspect of the photosynthetic characteristics of the leaf.
  The obtained result must be discussed in connection with the SPD of measuring light so as not to make biased evaluation caused by the interaction.

------

**Abbreviations**
BR-light: blue and red LED light,
Chl: chlorophyll,
ETR: electron transport rate,
FR: far-red,
LED: light-emitting diode,
*P*~n~: net photosynthetic rate,
PFD: photon flux density,
PPFD: photosynthetic photon flux density,
PSI: photosystem I,
PSII: photosystem II,
SPD: relative spectral PFD distribution

------

### 2016-08-04 Main.Rmd
英文構成を依頼 (Edanz)。3089 words

```{r Captions, eval = evalFig}
CapEED <-
  "Fig. 1  The excitation balance between photosystems in response to wavelength of measuring light. The spectrum was calculated from the absorbance spectra of PSII and PSI complexes in solvent (Hogewoning et al. 2012)."

CapETRs <-
  "Fig. 2  The conceptual diagrams of the effects of the excitation energy distribution between the photosystems (PSII and PSI) on the photosynthetic electron transport rate (ETR). Electron flow (grey lines) and energy flow (black lines) of leaves grown under PSII-light (A, B) and PSI-light (C, D) measured using PSII-light (A, C) and PSI-light (B, D) were shown. "

CapInteract <-
  "Fig. 3  The conceptual diagram of the photosynthetic electron transport rates per absorbed photons by the photosystems grown under PSII-light (PSII-leaves) and PSI-light (PSI-leaves) in response to the PSII/PSI-bised level of measuring light."

CapSPD <-
  'Fig. 4  The spectral photon flux density distributions of light provided by (a) fluorescent lamp (FL; FPL55EX-N<sup>1</sup>), metal halide lamp (MH; M220FCELS-W/BUD<sup>1</sup>), and, high-pressure sodium lamp (HPS; NH220FLS<sup>1</sup>), (b) blue (B; HBL3-3S55-LE<sup>2</sup>), red (R; SRK3-3A80-LE<sup>2</sup>), far-red (FR; L735-36AU<sup>3</sup>), and white (W; NSPW310DS<sup>4</sup>) light-emitting diodes, and (c) incident and leaf transmitted sunlight. The distributions at a photon flux density of 100 µmol m<sup>--2</sup> s<sup>--1</sup> within 400--750 nm are shown. The distribution of sunlight was adopted from JIS C 8904-3. The distribution of the leaf transmitted sunlight was calculated from that of sunlight and the transmittance spectrum of a cucumber leaf (Murakami et al. 2016). The far-red waveband (700--750 nm) is filled in grey. <sup>1</sup>IWASAKI ELECTRIC CO., LTD, Tokyo, Japan; <sup>2</sup>Tricon Co., Shimane, Japan; <sup>3</sup>Epitex Inc., Kyoto, Japan; <sup>4</sup>Nichia Chemical Industries Ltd., Tokushima, Japan.'
```

@@

Affiliations: ^1^Graduate School of Agricultural and Life Sciences, The University of Tokyo

Address: ^1^Yayoi, Bunkyo, Tokyo, 113--8657, Japan

e-mail: keach.murakami@gmail.com

------

**Abstract**

  The spectral photon flux density distributions (SPDs) of durign growth and for measurements do not only directly affect the net photosynthetic rate (*P*~n~) but also interacts on it.
  The plausible origin of the interaction, some situations in which the interaction should be concerned, and the selection of appropriate measuring light are summarized.
  *P*~n~ should be measured under *in situ* conditions depending on the purpose of the study.
  In prospective studies focusing on plant growth after the measurements, the measurements should be made under the SPD of light that the plant will be subject to.
  In retrospective studies aiming to elucidate causes of differences between the experimental groups, the measurements should be made under the SPDs of light that the plants have received during the treatments.
  In descriptive studies, *P*~n~ should be evaluated under several SPDs of measuring light to comprehend generalized characteristics.
  *P*~n~ under a single-pattern SPD of measuring light is only an aspect of the photosynthetic characteristics of the leaf.
  The obtained result must be discussed in connection with the SPD of measuring light so as not to make biased evaluation caused by the interaction.

------

**Abbreviations**
BR-light: blue and red LED light,
Chl: chlorophyll,
ETR: electron transport rate,
FR: far-red,
LED: light-emitting diode,
*P*~n~: net photosynthetic rate,
PFD: photon flux density,
PPFD: photosynthetic photon flux density,
PSI: photosystem I,
PSII: photosystem II,
SPD: relative spectral PFD distribution

------

  The photosynthetic rate is one of the most important and fundamental aspects for growth of plants.
  The rates are measured, evaluated, and compared among the leaves cultivated under different conditions.
  The measured rates are also used for the calculation of the other photosynthesis-related indices, such as light-, water-, and nitrogen-use efficiencies for photosynthesis.
  In agricultural and horticultural studies, the effectiveness of treatments is sometimes discussed based on the measured photosynthetic rates and calculated parameters. 
  Therefore, accurate measurements of the photosynthetic rates must be essential.

  A number of studies have reported that the relative spectral photon-flux-density (PFD) distribution (SPD) of light used for the measurement (i.e. measuring light or actinic light) affected leaf net photosynthetic rates (*P*~n~) [e.g. @McCree1972AM; @Inada1976PCP].
  To eliminate this direct effect from the comparison, *P*~n~ is usually measured under a common SPD of measuring light irrespective of leaf growth conditions in agricultural and horticultural studies.
  One of the most widely-used measuring light is mixture of blue and red light provided by LED light sources (BR-light) installed in commercial photosynthesis analyzing systems (e.g. LI6400 and LI6400XT, LI-COR Inc.; GFS-3000, Heinz Walz GmbH).
  The use of artificial light sources enables precise control of the photosynthetic PFD (PPFD) and SPD incident on the leaf and therefore ensure the reproducibility and reliability of the experiments.

  @Walters2005JXB pointed out that measuring photosynthetic rates with a SPD of light different from that of growth light do not necessarily reflect the functioning of photosynthesis under growth conditions.
  Our recent study, indeed, experimentally demonstrated this problem in the *P*~n~ measurements [@Murakami_et_al2016PP].
  In that experiment, cucumber seedlings were grown under white light-emitting diode (LED) light without and with supplemental far-red (FR) LED light (W and WFR), and subsequently *P*~n~ of the leaves were compared under BR-light and light with the SPD resembling that of sunlight (‘artificial’ sunlight).
  The *P*~n~ of W-leaves was greater than that of WFR-leaves under BR-light, while the rates were comparable under the artificial sunlight [@Murakami_et_al2016PP].
  Based on the results obtained from the measurement under BR-light, the prospective leaf photosynthetic rate of WFR-plants may be evaluated to be smaller than that of W-plants despite the comparable rates under sunlight.

  The effect of the SPD of growth light on *P*~n~ depends on the SPD of measuring light.
  In other words, the SPDs of growth light and measuring light interact on *P*~n~ of a leaf.
  In this short article, we introduce a plausible cause of the interaction---**the excitation balance between the photosystems**.
  We then suggest situations in which the interaction should be particularly cared.
  We also discuss the good practice for selecting of the SPD of measuring light for *P*~n~ measurements.
  The SPD of light affects photosynthesis through **several mechanisms other than the excitation balance**, such as stomatal responses [@Shimazaki_et_al2007AnnRev], photoinhibition [@Zavafer_et_al2015JPP], and vertical PFD profile within a leaf [@Terashima_et_al2009PCP].
  Although these subjects are not referred in this article, the cited articles are available for these topics.

  Fundamental knowledge about the photosynthetic electron transport is required to understand the mechanism of the interaction.
  Light energy absorbed by a leaf drives the photosynthetic electron transport, O~2~ evolution, and CO~2~ uptake.
  In higher plants, the photosynthetic electron transport chain is anchored by photochemical reactions that occur at two types of photosystems, PSII and PSI.
  The reactions are powered by excitation energy derived from absorbed photons.
  The excitation energy transferred to the reaction centers of the photosystems is consumed by the photochemical reactions.
  The serial photochemical reactions at PSII and PSI enables electron transfer from water to NADP^+^ (called the Z scheme).

  PSII and PSI represent different light absorption spectral distributions due to the difference in the compositions of binding pigments, mainly chl *a* and chl *b*.
  Within the chlorophyll (chl) absorption band (approximately 350--750 nm), longer wavelengths of light (> 680--690 nm) are estimated to be preferentially absorbed by PSI, and PSI is drastically overexcited [Fig. 1; @Evans_Anderson1987BBA; @Hogewoning_et_al2012PC; @Wientjes_et_al2013BBA; @Laisk_et_al2014BBA].
  This is because only chl *a* can absorb the longer wavelengths of light and PSI contains a greater amount of chl *a* than PSII.
  In contrast, monochromatic light at shorter wavelengths (< 680--690 nm) is estimated to be preferentially absorbed by PSII, or evenly absorbed by both photosystems [Fig. 1; @Evans_Anderson1987BBA; @Hogewoning_et_al2012PC; @Wientjes_et_al2013BBA; @Laisk_et_al2014BBA].
  These wavelength dependencies of the excitation is a determinant of the EED under a given SPD of light.
  In studies on the acclimation of the photosynthetic apparatus to the SPD of growth light, light with a given SPD is categorized as either PSII- or PSI-light according to whether the excitation energy is preferentially distributed to PSII or PSI [e.g. @Chow_et_al1990PNAS; @Melis1991BBA; @Pfannschmidt_et_al2001JBC; @Fan_et_al2007BBA; @Dietzel_et_al2008FJ; @Pfannschmidt_et_al2009AB; @Dietzel_et_al2011PC; @Hogewoning_et_al2012PC].
  This categorization is defined for a given leaf in the relative scale, not in the absolute scale.
  For instance, a SPD of light, which is evenly absorbed by PSII and PSI in PSII-light-grown leaves (Fig. 2A), can overexcite PSII in PSI-light-grown leaves (Fig. 2C).
  Thus, the terms ‘PSII-light’ and ‘PSI-light’ are used only in a relative context.

  Because the photosynthetic electron transport reactions occur in series, the electron transport rate (ETR) through the thylakoid membranes should be limited by the slowest step (Fig. 2).
  **When the excitation energy is in excess at PSII, the fewer energy distributed to PSI results in the smaller photochemical reaction rate in PSI.**
  **This shortage in PSI limits the ETR and therefore the photochemical quantum yield of PSII should be lowered (Fig. 2C).**
  When PSI absorbs the excess excitation energy, the energy distribution to PSII limits the ETR and the yield of PSI should be lowered (Fig. 2B).
  In both cases, the excess energy is dissipated mainly as heat and fluorescence, and thus the entire photosynthetic quantum yield---ETR per absorbed photons by the leaf---becomes smaller.
  Imbalanced excitation between the photosystems is supposed to harm leaves by generating reactive oxygen species, which cause oxidative damage to chloroplast components [for reviews, see @Asada1999AnnRev; @Asada2006PP].
  Balancing the excitation energy distribution (EED) between PSII and PSI is essential for plants to keep the high photosynthetic quantum yield.

  Apparently, the EED at a given SPD of light is also affected by the composition of the thylakoid components, especially by the stoichiometry between PSII and PSI.
  The stoichiometry seems to be adjusted to the SPD of growth light.
  Under PSII-light, the relative amount of the reaction center complex of PSII to that of PSI in leaves decreases; conversely, under PSI-light, the relative amount increases to achieve a balance [e.g. @Melis1991BBA; @Pfannschmidt_et_al1999Nature].
  As a result of these resposes adjusting the EED, the excitation spectrum (Fig. XXX) differs depending on the SPD of grown light.
  The adjustments in the EED properties might help the leaves to keep the high photosynthetic quantum yield under growth light [@Chow_et_al1990PNAS].
  In the short term within an hour, an imbalance in the EED is, at least partly, relieved by the reversible allocation of the light-harvesting antenna complex of PSII (LHCII) between PSII and PSI [state transition; for a review, see @Goldschmidt-Clermont_Bassi2015CurOpin].
  Although a slight imbalance in the EED might be compensated for by the state transitions, the long-term adjustments in the EED properties are supposed to occur when state transitions are insufficient to counterbalance the uneven EED [@Dietzel_et_al2008FJ].

  The SPD of growth light affects the EED properties of a leaf, which modifies the responses of ETR and thereby *P*~n~ to the SPD of measuring light.
  Thus, the SPDs of growth light and measuring light do not only directly affect the *P*~n~ but also indirectly affect it through their interaction.
  The expected interactions have been reported in several studies [@Chow_et_al1990PNAS; @Walters_Horton1995aPlanta; @Hogewoning_et_al2012PC; @Murakami_et_al2016PP].
  In their pioneering study, @Chow_et_al1990PNAS grew *Pisum sativum* plants under light provided by cool-white fluorescent lamps with yellow Plexiglas (PSII-light) and incandescent bulbs with red Plexiglas (PSI-light) and measured the photosynthetic quantum yield of O~2~ evolution---O~2~ evolution rate per absorbed photons by the leaf---under the PSII- and PSI-light reciprocally.
  When measured under the PSII-light, the yield was higher in the PSII-light-grown leaves; when measured under the PSI-light, the yield was higher in the PSI-light-grown leaves.
  Similar trends were observed in *Arabidopsis thaliana* [@Walters_Horton1995aPlanta] and *Cucumis sativus* in the photosynthetic quantum yield of CO~2~ uptake [@Hogewoning_et_al2012PC] and in the *P*~n~ [see also Introduction; @Murakami_et_al2016PP].

  These reports suggest that the EED properties of a leaf might be tuned to the PSII/PSI-biased level of growth light.
  It is expected that a leaf performs a higher ETR per absorbed photons by the photosystems under measuring light with a PSII/PSI-biased level similar to that of growth light (Fig. 3).
  When leaves grown under different SPDs of light are compared and evaluated under a specific SPD of light, the results should be inevitably biased depending on the SPD of measuring light.

  This interaction may have considerable impact on *P*~n~ especially measured under low PPFDs and/or high CO~2~ concentrations, where the ETR is a limiting factor for the photosynthetic CO~2~ fixation [@vonCaemmerer_Farquhar1981Planta].
  Under such conditions, any bias in the ETR is directly reflected in *P*~n~.
  Therefore, the *P*~n~ under these conditions should be measured with particular attention on the interaction.

  If the SPD of light that the leaves will be subject to is not predetermined, then the measurements should be made under several SPDs of light including PSII- and PSI-light.
  Researchers had better report the ‘general’ characteristics of the leaves in these descriptive studies.
  Therefore, the interaction should be tested so as not to make biased evaluation.
  If any the interaction, the results should be descriptively reported and should not be generalized.
  When the measurements were made only under a single-pattern of SPD of measuring light because of unavoidable circumstances, the light source must be declared in the materials and methods section so that readers can follow the SPD.

  The *P*~n~ under a single-pattern SPD of measuring light is only an aspect of the photosynthetic characteristics of the leaf.
  Therefore, the obtained result must be discussed in connection with the SPD of measuring light.
  Evaluation of the photosynthesis should be made under the *in situ* conditions or multi-pattern of SPDs of measuring light so that the evaluation is not biased by the interaction.
  Imitating the various SPDs of light incident on the leaf for *in situ* evaluation might be difficult or impossible from the technical reasons.
  In addition, measuring the *P*~n~ under multi-pattern of SPDs is time-, resource-, and labor-consuming.
  Although these two approaches might not always be applied for evaluation of the leaf *P*~n~, the interaction should be kept in mind to make circumspect conclusions.

```{r, eval = evalFig, fig.cap = CapEED}
EEDs
```

```{r, eval = evalFig, fig.cap = CapETRs}
knitr::include_graphics("FigETR.png")
```

```{r, eval = evalFig, fig.cap = CapInteract}
InteractionView
```

```{r, eval = evalFig, htmlcap = CapSPD}
SPDs
```

```{r, eval = evalFig, fig.cap = ""}
```

>>>>

  The photosynthetic rate is one of the most important and fundamental aspects for growth of plants.
  The rates are measured, evaluated, and compared among the leaves cultivated under different conditions.
  The measured rates are also used for the calculation of the other photosynthesis-related indices, such as photosynthetic light-, water-, and nitrogen-use efficiencies.
  In agricultural and horticultural studies, the effectiveness of treatments is sometimes discussed based on the measured photosynthetic rates and calculated indices. 
  Therefore, accurate measurements of the photosynthetic rates must be essential.

  A number of studies have reported that the relative spectral photon-flux-density (PFD) distribution (SPD) of light used for the measurement (i.e. measuring light or actinic light) affected leaf net photosynthetic rates (*P*~n~) [e.g. @McCree1972AM; @Inada1976PCP].
  To eliminate this direct effect from the comparison, *P*~n~ is usually measured under a common SPD of measuring light irrespective of leaf growth conditions in agricultural and horticultural studies.
  One of the most widely-used measuring light is mixture of blue and red light provided by LED light sources (BR-light) installed in commercial photosynthesis analyzing systems (e.g. LI6400 and LI6400XT, LI-COR Inc., Lincoln, NE; GFS-3000, Heinz Walz GmbH, Effeltrich, Germany).
  The use of artificial light sources enables precise control of the photosynthetic PFD (PPFD) and SPD incident on the leaf and therefore ensures the reproducibility and reliability of the experiments.

  @Walters2005JXB pointed out that measuring photosynthetic rates with a SPD of light different from that of growth light do not necessarily reflect the functioning of photosynthesis under growth conditions.
  Our recent study, indeed, experimentally demonstrated this problem in *P*~n~ measurements [@Murakami_et_al2016PP].
  In that experiment, cucumber seedlings were grown under white light-emitting diode (LED) light without and with supplemental far-red (FR) LED light (W and WFR), and subsequently *P*~n~ of the leaves were compared under BR-light and light with the SPD resembling that of sunlight (‘artificial’ sunlight).
  The *P*~n~ of W-grown-leaves was greater than that of WFR-grown-leaves under BR-light, while the rates were comparable under the artificial sunlight [@Murakami_et_al2016PP].
  Based on the results obtained from the measurement under BR-light, the prospective leaf photosynthetic rate of WFR-grown-plants may be evaluated to be smaller than that of W-grown-plants despite the comparable rates under sunlight.

  The effect of the SPD of growth light on *P*~n~ depends on the SPD of measuring light.
  In other words, the SPDs of growth light and measuring light interact on *P*~n~ of a leaf.
  In this short article, we describe a plausible mechanism of the interaction through the excitation balance between the photosystems.
  We then suggest situations in which the interaction should be particularly cared.
  We also discuss the good practice for selecting of the SPD of measuring light for *P*~n~ measurements.
  Several mechanisms other than the excitation balance, such as stomatal responses [@Shimazaki_et_al2007AnnRev], photoinhibition [@Zavafer_et_al2015JPP], and vertical PFD profile within a leaf [@Terashima_et_al2009PCP], affect photosynthesis through the SPD of measuring light.
  Although these subjects are not referred in this article, the cited articles are available for these topics.

  Fundamental knowledge about the photosynthetic electron transport is required to understand the mechanism of the interaction.
  Light energy absorbed by a leaf drives the photosynthetic electron transport, O~2~ evolution, and CO~2~ uptake.
  In higher plants, the photosynthetic electron transport chain is anchored by photochemical reactions that occur at two types of photosystems, PSII and PSI.
  The excitation energy derived from absorbed photons and transferred to the reaction centers of the photosystems is consumed by the photochemical reactions.
  The serial photochemical reactions at PSII and PSI enable electron transfer from water to NADP^+^, called the Z scheme.

  PSII and PSI represent different spectral light absorption distributions due to the difference in the compositions of binding pigments, mainly chl *a* and chl *b*.
  Within the chlorophyll (chl) absorption band (approximately 350--750 nm), longer wavelengths of light (> 680--690 nm) are estimated to be preferentially absorbed by PSI, and PSI is drastically overexcited [Fig. 1; @Evans_Anderson1987BBA; @Hogewoning_et_al2012PC; @Wientjes_et_al2013BBA; @Laisk_et_al2014BBA].
  This is because only chl *a* can absorb longer wavelengths of light and PSI contains a greater amount of chl *a* than PSII.
  In contrast, monochromatic light at shorter wavelengths (< 680--690 nm) is estimated to be preferentially absorbed by PSII, or evenly absorbed by both photosystems [Fig. 1; @Evans_Anderson1987BBA; @Hogewoning_et_al2012PC; @Wientjes_et_al2013BBA; @Laisk_et_al2014BBA].
  These wavelength dependencies of the excitation balance between PSII and PSI determine the excitation energy distribution (EED) under a given SPD of light.
  Light with a given SPD is sometimes categorized as either PSII- or PSI-light according to whether the excitation energy is preferentially distributed to PSII or PSI [e.g. @Chow_et_al1990PNAS; @Melis1991BBA; @Pfannschmidt_et_al2001JBC; @Fan_et_al2007BBA; @Dietzel_et_al2008FJ; @Pfannschmidt_et_al2009AB; @Dietzel_et_al2011PC; @Hogewoning_et_al2012PC].

  Because the photosynthetic electron transport reactions occur in series, the electron transport rate (ETR) through the thylakoid membrane should be limited by the slowest step (Fig. 2).
  When the excitation energy is in excess at PSII (i.e. under PSII-light), the fewer excitation energy distributed to PSI results in the smaller photochemical reaction rate in PSI than that in PSII.
  This shortage in the EED to PSI limits the ETR and therefore the photochemical quantum yield of PSII should be lowered (Fig. 2C).
  When PSI absorbs the excess excitation energy (i.e. under PSI-light), the excitation energy distributed to PSII limits the ETR and the yield of PSI should be lowered (Fig. 2B).
  In both cases, the excess energy is dissipated mainly as heat and fluorescence, and thus the entire photosynthetic quantum yield---ETR per absorbed photons by the leaf---becomes smaller.
  Therefore, balancing the EED between PSII and PSI is essential for plants to keep the high photosynthetic quantum yield.
  Imbalanced excitation between the photosystems is supposed to harm leaves by generating reactive oxygen species, which cause oxidative damage to chloroplast components [for reviews, see @Asada1999AnnRev; @Asada2006PP].

  Apparently, the EED at a given SPD of light is also affected by the composition of the thylakoid components, especially by the stoichiometry between PSII and PSI.
  The stoichiometry seems to be adjusted to the SPD of growth light.
  Under PSII-light, the relative amount of the reaction center complex of PSII to that of PSI in leaves decreases; conversely, under PSI-light, the relative amount increases to achieve a balance [e.g. @Melis1991BBA; @Pfannschmidt_et_al1999Nature].
  These adjustments in the EED properties might help the leaves to keep the high photosynthetic quantum yield under growth light [@Chow_et_al1990PNAS].
  As a result of these resposes adjusting the EED properties of a leaf, the spectrum of excitation balance (Fig. 1) differs depending on the SPD of grown light.
  The categories of light---‘PSII-light’ and ‘PSI-light’---are defined for a given leaf in the relative scale, not in the absolute scale.
  For instance, a SPD of light, which is evenly absorbed by PSII and PSI in PSII-light-grown leaves (Fig. 2A), can overexcite PSII in PSI-light-grown leaves (Fig. 2C).
  Therefore, the terms ‘PSII-light’ and ‘PSI-light’ are used only in a relative context.
  In the short term within an hour, an imbalance in the EED is, at least partly, relieved by the reversible allocation of the light-harvesting antenna complex of PSII (LHCII) between PSII and PSI [state transition; for a review, see @Goldschmidt-Clermont_Bassi2015CurOpin].
  Although a slight imbalance in the EED might be compensated for by the state transitions, the long-term adjustments in the EED properties are supposed to occur when state transitions are insufficient to counterbalance the uneven EED [@Dietzel_et_al2008FJ].

  The SPD of growth light affects the EED properties of a leaf, which modifies the responses of ETR and thereby *P*~n~ to the SPD of measuring light.
  Thus, the SPDs of growth light and measuring light do not only directly affect the *P*~n~ but also indirectly affect it through their interaction.
  The expected interaction has been reported in several studies [@Chow_et_al1990PNAS; @Walters_Horton1995aPlanta; @Hogewoning_et_al2012PC; @Murakami_et_al2016PP].
  In their pioneering study, @Chow_et_al1990PNAS grew *Pisum sativum* plants under light provided by cool-white fluorescent lamps with yellow Plexiglas (PSII-light) and incandescent bulbs with red Plexiglas (PSI-light) and measured the photosynthetic quantum yield of O~2~ evolution---O~2~ evolution rate per absorbed photons by the leaf---under the PSII- and PSI-light reciprocally.
  When measured under the PSII-light, the yield was higher in the PSII-light-grown leaves; when measured under the PSI-light, the yield was higher in the PSI-light-grown leaves.
  Similar trends were observed in *Arabidopsis thaliana* [@Walters_Horton1995aPlanta] and *Cucumis sativus* in the photosynthetic quantum yield of CO~2~ uptake [@Hogewoning_et_al2012PC] and in the *P*~n~ [see also Introduction; @Murakami_et_al2016PP].

  These reports suggest that the EED properties of a leaf might be tuned to the PSII/PSI-biased level of growth light.
  It is expected that a leaf performs a higher ETR per absorbed photons by the leaf under measuring light with a PSII/PSI-biased level similar to that of growth light (Fig. 3).
  When leaves grown under different SPDs of light are compared and evaluated under a specific SPD of light, the results should be inevitably biased depending on the SPD of measuring light.

  The interaction may have considerable impact on *P*~n~ especially measured under low PPFDs and/or high CO~2~ concentrations, where the ETR is a limiting factor for the photosynthetic CO~2~ fixation [@vonCaemmerer_Farquhar1981Planta].
  Under such conditions, any bias in the ETR is directly reflected in *P*~n~.
  Therefore, the *P*~n~ under these conditions should be measured with particular attention on the interaction.

  On the other hand, in descriptive studies making no assumption as to *in situ* condition, the measurements should be made under several SPDs of light including PSII- and PSI-light.
  Researchers had better report the ‘general’ characteristics of the leaves in these studies.
  Therefore, the interaction should be tested so as not to make biased evaluation.
  If any the interaction, the results should be descriptively reported and should not be generalized.
  When the measurements were made only under a single-pattern of SPD of measuring light because of unavoidable circumstances, the light source must be declared in the materials and methods section so that readers can follow the SPD.

  The *P*~n~ under a single-pattern SPD of measuring light is only an aspect of the photosynthetic characteristics of the leaf.
  Therefore, the obtained result must be discussed in connection with the SPD of measuring light.
  Evaluation of the photosynthesis should be made under the *in situ* conditions or multi-pattern of SPDs of measuring light so that the evaluation is not biased by the interaction.
  Imitating the various SPDs of light incident on the leaf for *in situ* evaluation might be difficult or impossible from the technical reasons.
  In addition, measuring the *P*~n~ under multi-pattern of SPDs is time-, resource-, and labor-consuming.
  Although these two approaches might not always be applied for evaluation of leaf *P*~n~, the interaction should always be kept in mind to make circumspect conclusions.

```{r Captions}
CapEED <-
  "Fig. 1  Excitation balance between photosystems in response to wavelength of measuring light. The spectrum was calculated from absorbance spectra of PSII and PSI complexes in solvent (Hogewoning et al. 2012)."

CapETRs <-
  "Fig. 2  Conceptual diagrams of the effects of the excitation energy distribution between the photosystems (PSII and PSI) on the photosynthetic electron transport rate (ETR). Electron flow (grey lines) and energy flow (black lines) of leaves grown under PSII-light (A, B) and PSI-light (C, D) measured using PSII-light (A, C) and PSI-light (B, D) were shown. "

CapInteract <-
  "Fig. 3  Conceptual diagram of the photosynthetic electron transport rates per absorbed photons by the leaf grown under PSII-light (PSII-leaves) and PSI-light (PSI-leaves) in response to the PSII/PSI-bised level of measuring light."

CapSPD <-
  'Fig. 4  Spectral photon flux density distributions of light provided by (a) fluorescent lamp (FL; FPL55EX-N<sup>1</sup>), metal halide lamp (MH; M220FCELS-W/BUD<sup>1</sup>), and, high-pressure sodium lamp (HPS; NH220FLS<sup>1</sup>), (b) blue (B; HBL3-3S55-LE<sup>2</sup>), red (R; SRK3-3A80-LE<sup>2</sup>), far-red (FR; L735-36AU<sup>3</sup>), and white (W; NSPW310DS<sup>4</sup>) light-emitting diodes, and (c) incident and leaf transmitted sunlight. The distributions at a photon flux density of 100 µmol m<sup>--2</sup> s<sup>--1</sup> within 400--750 nm are shown. The far-red waveband (700--750 nm) is filled in grey. The distribution of sunlight was adopted from the International Electrotechnical Commission Standard 60904–3 [@IEC2007]. The distribution of the leaf transmitted sunlight was calculated from that of incident sunlight and the transmittance spectrum of a cucumber leaf (Murakami et al. 2016).<br><sup>1</sup>IWASAKI ELECTRIC CO., LTD, Tokyo, Japan; <sup>2</sup>Tricon Co., Shimane, Japan; <sup>3</sup>Epitex Inc., Kyoto, Japan; <sup>4</sup>Nichia Chemical Industries Ltd., Tokushima, Japan.'
```

@@

```{r, eval = evalFig, html.cap = CapEED}
EEDs
```

```{r, eval = evalFig, html.cap = CapETRs}
knitr::include_graphics("./Figs/FigETR.png")
```

```{r, eval = evalFig, html.cap = CapInteract}
InteractionView
```

```{r, eval = evalFig, html.cap = CapSPD}
SPDs
```
